---
title: "Exploratory analysis"
author: "Nirodha Epasinghe"
output: html_document
date: '2022-07-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

```{r prep_data}
train_data <- read.csv(file = here::here("Data", "train.csv"))
test_data <- read.csv(file = here::here("Data", "test.csv"))

myvars <- names(train_data)[c(1:38, 81)]

train_data_sub <- train_data %>% 
  select(all_of(myvars))

# select only factors
train_data_sub[sapply(train_data_sub, is.character)] <- lapply(train_data_sub[
  sapply(train_data_sub, is.character)], as.factor)

# Select only numeric variables
train_data_int <- train_data_sub %>% 
  select_if(~class(.) == 'integer')

predictors <- names(train_data_sub) 
predictors <- predictors[!predictors %in% c("SalePrice")]

dependent <- "SalePrice"
```

### Visualising data

```{r var_set1, out.width='100%'}
train_data_sub %>% 
  select({{dependent}}, all_of(predictors[1:5])) %>% 
  GGally::ggpairs()


```

MSZoning, LotFrontage and LotArea are showing some relationship with the SalePrice


```{r var_set2, out.width='100%'}

train_data_sub %>% 
  select({{dependent}}, all_of(predictors[6:9])) %>% 
  GGally::ggpairs()


```

Street, Alley, LotShape and LandContour are important

```{r var_set3, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[10:12])) %>% 
  GGally::ggpairs()


```

Utilities, LotConfig, LandSlope are important

```{r var_set4, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[14:18])) %>% 
  GGally::ggpairs()


```

Condition1, Condition2, BldgType, HouseStyle are important

```{r var_set15, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[19:23])) %>% 
  GGally::ggpairs()


```
YearBuilt, YearRemodAdd, RoofStyle, RoofMatl are important

```{r var_set6, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[26:29])) %>% 
  GGally::ggpairs()


```

ExterQual, ExterCond are important


```{r var_set7, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[30:34])) %>% 
  GGally::ggpairs()


```


Foundation, BsmtQual, BsmtCond, BsmtExposure, BsmtFinType1 are important

```{r var_set8, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[35:38])) %>% 
  GGally::ggpairs()
```

BsmtUnfSF is important. 
