---
title: "Exploratory analysis"
author: "Puwasala Gamakumara"
date: "2022-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

```{r prep_data}
train_data <- read.csv(file = here::here("Data", "train.csv"))
test_data <- read.csv(file = here::here("Data", "test.csv"))

myvars <- names(train_data)[(40:81)]

train_data_sub <- train_data %>% 
  select(all_of(myvars))

train_data_sub <- train_data_sub %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate_if(is.integer, as.numeric) %>% 
  mutate(BsmtFullBath = factor(BsmtFullBath),
         BsmtHalfBath = factor(BsmtHalfBath),
         FullBath = factor(FullBath),
         HalfBath = factor(HalfBath),
         BedroomAbvGr = factor(BedroomAbvGr),
         KitchenAbvGr = factor(KitchenAbvGr),
         TotRmsAbvGrd = factor(TotRmsAbvGrd),
         Fireplaces = factor(Fireplaces))


predictors <- names(train_data_sub) 
predictors <- predictors[!predictors %in% c("SalePrice")]

dependent <- "SalePrice"
```

### Visualising data

```{r var_set1, out.width='100%'}
train_data_sub %>% 
  select({{dependent}}, all_of(predictors[1:5])) %>% 
  GGally::ggpairs()


```

Heating, HeatingQC, CantralAir, Electrical and 1stFlrSF are showing some relationship with the SalePrice


```{r var_set2, out.width='100%'}

train_data_sub %>% 
  select({{dependent}}, all_of(predictors[6:10])) %>% 
  GGally::ggpairs()


```

2ndFlrSF, GrLivArea, BsmtFullBath, BsmtHalfBath are important

```{r var_set3, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[11:15])) %>% 
  GGally::ggpairs()


```

FullBath, HalfBath, BedroomAbvGr, KitchenQual are important

```{r var_set4, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[16:20])) %>% 
  GGally::ggpairs()


```

TotRmsAbvGrd, Fireplaces, FireplaceQu, GarageType are important

```{r var_set15, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[21:25])) %>% 
  GGally::ggpairs()


```

GarageFinish, GarageCars, GarageArea are important

```{r var_set6, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[26:30])) %>% 
  GGally::ggpairs()


```

WoodDeckSF is important


```{r var_set7, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[31:35])) %>% 
  GGally::ggpairs()


```


PoolQC is important

```{r var_set8, out.width='100%'}


train_data_sub %>% 
  select({{dependent}}, all_of(predictors[36:40])) %>% 
  GGally::ggpairs()
```

MoSold, YrSold, SaleType are important
